\documentclass[11pt]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, left=1.06cm, top=1.7cm, right=1.06cm, bottom=1.5cm]{geometry}
\usepackage{fontspec}

\usepackage[bidi=basic, provide=*]{babel}

\babelprovide[import, onchar=ids fonts]{english}

% Set default/Latin font to Sans Serif in the main (rm) slot
\babelfont{rm}{Noto Sans}

% Add because we replaced the legacy list behavior
\usepackage{enumitem}
\setlist[itemize]{label=-}
% --- END UNIVERSAL PREAMBLE BLOCK ---

\usepackage{hyperref}
\setlength{\parindent}{0pt}

\begin{document}
\begin{center}
    \textbf{\LARGE Miguel Angel Bravo Vidales}\\ 
    \vspace{4pt}
    \hrulefill
\end{center}

\begin{center}
    San Luis Potosí, SLP, México \textbullet \ x@mackaber.me \textbullet \ +52 444 444 7397 \textbullet \ linkedin.com/in/mackaber \textbullet \ github.com/mackaber
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{Tecnológico de Monterrey (ITESM)} \hfill Monterrey, NL

M.S. in Computer Science (Focus on Artificial Intelligence and Machine Learning) \hfill Dec 2020

\vspace{10pt}

\textbf{Tecnológico de Monterrey (ITESM)} \hfill	San Luis Potosí, SLP

B.S. in Information Technology and Communications \hfill Dec 2013

\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}

\textbf{Tecnológico de Monterrey (ITESM)} \hfill San Luis Potosí, SLP

\textbf{High School Professor} \hfill August 2025 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Instructed high school students in software development, covering programming fundamentals, logic building, and practical application design.
\end{itemize}

\vspace{8pt}

\textbf{Encora, Inc.} \hfill Remote

\textbf{AWS re/Start Instructor} \hfill February 2025 – June 2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Delivered comprehensive cloud computing training to a cohort of students, covering core AWS services, networking, security, and Linux/Python fundamentals.
    \item Guided students through practical lab exercises to prepare them for the AWS Certified Cloud Practitioner exam and transition into entry-level cloud computing roles.
\end{itemize}

\vspace{8pt}

\textbf{Spark Tech Staff} \hfill January 2025 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Mentored new hires in data structures and algorithms through the internal Algorithm School Program, accelerating their readiness for client matching.
\end{itemize}

\vspace{8pt}

\textbf{Full Stack Developer} \hfill January 2021 – 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Built AI-powered development tools using Python, LangChain, Streamlit, and the OpenAI API, automating the generation of React and React Native (Expo) template applications.
    \item Maintained and optimized a legacy travel loyalty application (Arrivia), implementing resource monitoring via Azure AppInsights to identify and resolve high-consumption tasks.
    \item Developed robust data processing pipelines for a telehealth platform (MDLive), processing patient records and building doctor incentive systems using Ruby on Rails, Redis, and RabbitMQ.
\end{itemize}

\vspace{8pt}

\textbf{DEV.f} \hfill Remote

\textbf{Professor of Web Development} \hfill August 2021 – March 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Taught comprehensive 6-month full-stack web development bootcamps covering HTML, CSS, JavaScript, Node.js, and React.
    \item Guided students with no prior software development background through practical, hands-on projects to build industry-ready portfolios.
\end{itemize}

\vspace{8pt}

\textbf{Continental} \hfill San Luis Potosí, SLP

\textbf{Full Stack Developer (Freelancer)} \hfill January 2014 – December 2017
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed and maintained the Android application for a conveyor administration platform.
    \item Built a desktop integration service using Ruby to connect new interfaces with existing legacy applications.
\end{itemize}

\vspace{8pt}

\textbf{Winero} \hfill San Luis Potosí, SLP

\textbf{Co-founder, CTO \& Full Stack Developer} \hfill July 2013 – December 2016
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Co-founded a loyalty programs platform, architecting the data structures, backend system (Ruby on Rails, PostgreSQL), and performance analytics dashboard.
\end{itemize}

\vspace{12pt}

\begin{center}
    \textbf{Leadership \& Activities}
\end{center}

\textbf{Tech Communities \& Events}	\hfill Mexico

\textbf{Speaker, Mentor \& Co-founder} \hfill 2013 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Participated in over 20 Hackathons (winning 2 and mentoring 10), including Startup Weekend, AngelHack, and Talent Hackathon.
    \item Delivered 15+ talks and workshops on software engineering and AI at major tech events such as TalentLand, Nerdearla, and NerdyTalks.
    \item Co-founded ``Comunidad Código,'' a local developers' association, and actively contributed to the Tuna Valley initiative.
\end{itemize}

\vspace{12pt}

\begin{center}
    \textbf{Skills, Certifications \& Interests}
\end{center}

\textbf{Certifications:} AWS Solutions Architect (2025), Azure AI Engineer Associate (AI-102) (2024, Renewed 2025)

\textbf{Technical Skills:} Ruby, Python, JavaScript, Java, SQL, Ruby on Rails, Node.js, React, TensorFlow, Docker, AWS, Azure, Git, LangChain, Redis, RabbitMQ

\textbf{Languages:} Spanish (Native), English (Fluent)

\end{document}